NumPy---Array Programming in Python

### 2020-01-20 body.tex
More work on Fig. 2
Mention we are community developed

Today, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2019scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It consists of an multidimensional array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the {\it de facto} exchange format for array data in Python.
The library has such widespread adoption that not only the array object but also its
{\it Application Programming Interface} (API) has become ubiquitous as
a language for array programming.

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{static/sketches/duck-arrays}
  \caption{\textbf{Interoperability.} \fixme{This figure needs work.}}  \label{fig:duck-arrays}
\end{figure*}

>>>>

Today, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2019scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It is a community developed, open source library, which provides a
multidimensional Python array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the {\it de facto} exchange format for array data in Python.
The library has such widespread adoption that not only the array object but also its
{\it Application Programming Interface} (API) has become ubiquitous as
a language for array programming.

@@

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{static/sketches/duck-arrays}
  \caption{\textbf{Interoperability.} \fixme{This figure needs work.}}\label{fig:duck-arrays}
\end{figure}
